### 2014-06-08 old/drafts/ijcai2013/ResponsesToReviewers.txt

Draft responses to IJCAI 2013 Review

overall common criticisms that should be addressed: 
1) is the work original (1, 4)?
2) how is the work related to ILP and predicate invention (1)
3) how is the work related to Chaitin's Algorithmic Complexity Theory (4)
4)

############################## Response to reviewer 1 ##############################
Main issue: What is the relationship to ILP?

Response: The reviewer is right to raise a connection between our work
and predicate invention in ILP, and we will revise the paper to note
this. However, while predicate invention in ILP is motivated by some
of the same considerations which motivate our work, the
learning framework in ILP is quite different from ours. ILP concerns
learning FOL theories from positive and negative
examples; our framework learns functional programs with respect to a
blackbox evaluator. This results in two main
differences. First, our framework is easily applicable to
both traditional ILP problems (like the boolean circuit learning
example) and problems more commonly found in statistical learning or
genetic programming (like the symbolic regression example). The second
and more crucial difference is that our choice of a functional
programming language makes it natural to capture reusable concepts as
higher-order functions (see, for example, the learned concept $E_1$ or
$E_2$ in Figure 4).

############################## Response to reviewer 2 ##############################
Main issue: Why not do a proper bayesian thing? Statistical discovery?

Response: The reviewer wonders about the algorithm's scalability and
points out that a sufficient number of solutions need to be found by
brute force search for the algorithm to work: we agree with this and
wish to emphasize that it is precisely the presence of some easy
problems that enables the algorithm to initially bootstrap an
effective grammar.

We agree that our approach can be framed as a statistical discovery
technique in which we iteratively re-estimate a stochastic grammar. We
are currently investigating this and will revise the paper to note
this interpretation. However, generating directly from this grammar,
as the reviewer suggests, instead of enumerating in a best-first
manner exacerbates the "needle-in-a-haystack" problem that our
algorithm faces; by enumerating programs, we are able to exhaustively
cover a large part of the prior mass of our stochastic grammar. We are
working to determine the advantages and disadvantages of
these two approaches.

############################## Response to reviewer 3 ##############################
Main issue: Why not use mdl measure like -log(p) instead of counting nodes.

Response: We would like to respond particularly to the reviewer's
question of why an mdl measure such as -log p was not used instead of
counting the nodes of the trees in Section 3.4. We agree with the
reviewer that this approach would be more elegant, and we will revise
the paper to make note of this. In order to take into account the
possibility of new rules (i.e. concept learning), however, we would
need to place a prior distribution over grammars (see, also, the
response to reviewer 2). This would likely require an expensive and
potentially inaccurate Monte Carlo approximation. We found the proxy
calculation of counting the number of unique subtrees in a set of
solutions to be a simple, intuitive, and elegant computation that gets
at the compressibility of the data.

############################## Response to reviewer 4 ##############################
Main issues: 1) Does this extend to noisy data. 2) What about Chaitin? (refer to response to reviewer 1).

Response: We understand the reviewer's concerns that a) this work has
similarities to Chaitin's Algorithmic Information Theory framework and
that b) that it is not clear in the paper how to extend this work to
noisy data. The reviewer is right that our approach is similar in
spirit to some of Chaitin's theoretical work, and his work will be
cited prominently, but our emphasis here is a novel search algorithm
that allows us to quickly bootstrap hundreds of programs for many
related tasks.

Dealing with noisy data requires one to choose a function that scores
candidate solutions to a task. We emphasize the aspects of our
approach that are independent of this, but there are straightforward
ways to extend our algorithm to noisy data. The most way natural is to
weight the subtree counting in section 3.4 by the chosen scoring
function. The paper will be revised to reflect this.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
TODO: implement josh's notes on this:

Notes from Josh: "We will revise the paper to note the The reviewers
are right to raise a connection to ILP and we will revise the paper to
note this, and we will revise the paper to note this, but we wills
tress the following differents.

Some of the same considerations not all
First order logic vs FOL.

We agree with the reviewer and we are currently investigating
(stochastic model thing) maybe move the we are going to do this part
to the start.

We will focus on this initially.

Typo "we would like to respond"

Can we argue about how the number of subtrees relating to the
nonparametric distribution. We will revise the paper to discuss this.
We do see what we are doing as an approximation to all that stuff, and
we will revise the paper to reflect that.

"It was not clear in our paper" instead of "It is not clear." and we
will revise the paper to reflect this. For the noisy data part.

Chaitin, should be cited prominently in the paper and we will.

"We believe there are straightforward ways" --> there are
straightforward ways and we are currently exploring them, and we will
revise the paper to reflect this.

### 2014-06-08 old/drafts/aistats2013/abstracts.tex
Moved everything into an a new 'old' directory.

% If your paper is accepted, change the options for the package
% aistats2014 as follows:
%
%\usepackage[accepted]{aistats2014}
%
% This option will print headings for the title of your paper and
% headings for the authors names, plus a copyright note at the end of
% the first column of the first page.

@@

% If your paper is accepted and the title of your paper is very long,
% the style will print as headings an error message. Use the following
% command to supply a shorter title of your paper so that it can be
% used as headings.
%
%\runningtitle{I use this title instead because the last one was very long}

% If your paper is accepted and the number of authors is large, the
% style will print as headings an error message. Use the following
% command to supply a shorter version of the authors names so that
% they can be used as headings (for example, use only the surnames)
%
%\runningauthor{Surname 1, Surname 2, Surname 3, ...., Surname n}

@@

\aistatstitle{Symbolic Density Estimation: Uncovering the code.}

@@

\begin{abstract}
  The Abstract paragraph should be indented 0.25 inch (1.5 picas) on
  both left and right-hand margins. Use 10~point type, with a vertical
  spacing of 11~points.  The {\bf Abstract} heading must be centered,
  bold, and in point size 12. Two line spaces precede the
  Abstract. The Abstract must be limited to one paragraph.
\end{abstract}

\section{GENERAL FORMATTING INSTRUCTIONS}

Both submitted and camera-ready versions of the paper are 8 pages,
plus any additional pages needed for references.

Papers are in 2 columns with the overall line width of 6.75~inches (41~picas). Each column is 3.25~inches wide (19.5~picas).  The space
between the columns is .25~inches wide (1.5~picas).  The left margin is 1~inch (6~picas).  Use 10~point type with a vertical spacing of
11~points. Times Roman is the preferred typeface throughout.

Paper title is 16~point, caps/lc, bold, centered between 2~horizontal rules.  Top rule is 4~points thick and bottom rule is 1~point thick.
Allow 1/4~inch space above and below title to rules.

Author descriptions are center-justified, initial caps.  The lead
author is to be listed first (left-most), and the Co-authors are set
to follow.  If up to three authors, use a single row of author
descriptions, each one center-justified, and all set side by side;
with more authors or unusually long names or institutions, use more
rows.  (But, do not include author names in the initial double-blind
submission!  Instead leave a row of ``Anonymous Author'' descriptions
as above.)

One-half line space between paragraphs, with no indent.

\section{FIRST LEVEL HEADINGS}

First level headings are all caps, flush left, bold, and in point size
12. One line space before the first level heading and 1/2~line space
after the first level heading.

\subsection{Second Level Heading}

Second level headings are initial caps, flush left, bold, and in point
size 10. One line space before the second level heading and 1/2~line
space after the second level heading.

\subsubsection{Third Level Heading}

Third level headings are flush left, initial caps, bold, and in point
size 10. One line space before the third level heading and 1/2~line
space after the third level heading.

\paragraph{Fourth Level Heading}

Fourth level headings must be flush left, initial caps, bold, and
Roman type.  One line space before the fourth level heading, and
place the section text immediately after the heading with, no line
break, but an 11 point horizontal space.

\subsection{CITATIONS, FIGURES, REFERENCES}

\subsubsection{Citations in Text}

Citations within the text should include the author's last name and
year, e.g., (Cheesman, 1985). References should follow any style that
you are used to using, as long as their style is consistent throughout
the paper.  Be sure that the sentence reads correctly if the citation
is deleted: e.g., instead of ``As described by (Cheesman, 1985), we
first frobulate the widgets,'' write ``As described by Cheesman
(1985), we first frobulate the widgets.''  Be sure to avoid
accidentally disclosing author identities through citations.

\subsubsection{Footnotes}

Indicate footnotes with a number\footnote{Sample of the first
  footnote.} in the text. Use 8 point type for footnotes. Place the
footnotes at the bottom of the column in which their markers appear,
continuing to the next column if required. Precede the footnote
section of a column with a 0.5 point horizontal rule 1~inch (6~picas)
long.\footnote{Sample of the second footnote.}

\subsubsection{Figures}

All artwork must be centered, neat, clean, and legible.  All lines
should be very dark for purposes of reproduction, and art work should
not be hand-drawn.  Figures may appear at the top of a column, at the
top of a page spanning multiple columns, inline within a column, or
with text wrapped around them, but the figure number and caption
always appear immediately below the figure.  Leave 2 line spaces
between the figure and the caption. The figure caption is initial caps
and each figure should be numbered consecutively.

Make sure that the figure caption does not get separated from the
figure. Leave extra white space at the bottom of the page rather than
splitting the figure and figure caption.
\begin{figure}[h]
\vspace{.3in}
\centerline{\fbox{This figure intentionally left non-blank}}
\vspace{.3in}
\caption{Sample Figure Caption}
\end{figure}

\subsubsection{Tables}

All tables must be centered, neat, clean, and legible. Do not use hand-drawn tables. Table number and title always appear above the table.
See Table~\ref{sample-table}.

One line space before the table title, one line space after the table title, and one line space after the table. The table title must be
initial caps and each table numbered consecutively.

\begin{table}[h]
\caption{Sample Table Title} \label{sample-table}
\begin{center}
\begin{tabular}{ll}
{\bf PART}  &{\bf DESCRIPTION} \\
\hline \\
Dendrite         &Input terminal \\
Axon             &Output terminal \\
Soma             &Cell body (contains cell nucleus) \\
\end{tabular}
\end{center}
\end{table}

\section{SUPPLEMENTARY MATERIAL}

If you need to include additional appendices during submission, you
can include them in the supplementary material file.

\newpage

\section{INSTRUCTIONS FOR CAMERA-READY PAPERS}

For the camera-ready paper, if you are using \LaTeX, please make sure
that you follow these instructions.  (If you are not using \LaTeX,
please make sure to achieve the same effect using your chosen
typesetting package.)

\begin{enumerate}
    \item Install the package \texttt{fancyhdr.sty}. The
    \texttt{aistats2014.sty} file will make use of it.
    \item Begin your document with
    \begin{flushleft}
    \texttt{\textbackslash documentclass[twoside]\{article\}}\\
    \texttt{\textbackslash usepackage[accepted]\{aistats2014\}}
    \end{flushleft}
    The \texttt{twoside} option for the class article allows the
    package \texttt{fancyhdr.sty} to include headings for even and odd
    numbered pages. The option \texttt{accepted} for the package
    \texttt{aistats2014.sty} will write a copyright notice at the end of
    the first column of the first page. This option will also print
    headings for the paper.  For the \emph{even} pages, the title of
    the paper will be used as heading and for \emph{odd} pages the
    author names will be used as heading.  If the title of the paper
    is too long or the number of authors is too large, the style will
    print a warning message as heading. If this happens additional
    commands can be used to place as headings shorter versions of the
    title and the author names. This is explained in the next point.
    \item  If you get warning messages as described above, then
    immediately after $\texttt{\textbackslash
    begin\{document\}}$, write
    \begin{flushleft}
    \texttt{\textbackslash runningtitle\{Provide here an alternative shorter version of the title of your
    paper\}}\\
    \texttt{\textbackslash runningauthor\{Provide here the surnames of the authors of your paper, all separated by
    commas\}}
    \end{flushleft}
    The text that appears as argument in \texttt{\textbackslash
      runningtitle} will be printed as a heading in the \emph{even}
    pages. The text that appears as argument in \texttt{\textbackslash
      runningauthor} will be printed as a heading in the \emph{odd}
    pages.  If even the author surnames do not fit, it is acceptable
    to give a subset of author names followed by ``et al.''

    \item Use the file sample\_paper.tex as an example.

    \item Both submitted and camera-ready versions of the paper are 8
      pages, plus any additional pages needed for references.

    \item If you need to include additional appendices,
      you can include them in the supplementary
      material file.

    \item Please, don't change the layout given by the above
      instructions and by the style file.

\end{enumerate}

\subsubsection*{Acknowledgements}

Use unnumbered third level headings for the acknowledgements.  All
acknowledgements go at the end of the paper.  Be sure to omit any
identifying information in the initial double-blind submission!

\subsubsection*{References}

References follow the acknowledgements.  Use an unnumbered third level
heading for the references section.  Any choice of citation style is
acceptable as long as you are consistent.  Please use the same font
size for references as for the body of the paper---remember that
references do not count against your page length total.

J.~Alspector, B.~Gupta, and R.~B.~Allen (1989). Performance of a
stochastic learning microchip.  In D. S. Touretzky (ed.), {\it
  Advances in Neural Information Processing Systems 1}, 748-760.  San
Mateo, Calif.: Morgan Kaufmann.

F.~Rosenblatt (1962). {\it Principles of Neurodynamics.} Washington,
D.C.: Spartan Books.

G.~Tesauro (1989). Neurogammon wins computer Olympiad.  {\it Neural
  Computation} {\bf 1}(3):321-323.

>>>>

@@

@@

\aistatstitle{Symbolic Density Estimation: Uncovering the Code.}

@@

\begin{abstract}
One prominent view in Machine Learning is that to make accurate predictions and generalizations from data, we need to learn the latent probabilistic generative models that give rise to the data we observe. Graphical models and neural networks

\end{abstract}

\begin{abstract}

\end{abstract}
